Policy Gradient Algorithms

### 2019-03-18 pge-mattis.tex
Clean up a sentence

\paragraph{Episode-based updates.} 
A very general optimization approach to this optimization problem are episodic algorithms. 
We take a search distribution $p(\theta|\omega)$ over the parameter space of the policy class $\pi$ of the acting policy, and sample policies from that distribution. 
The policy class $\pi$ is most often chosen deterministic. 
Using these policies, we sample trajectories $\tau$, and update the search policy using the returns of our sampled roll-outs
\begin{equation}
	\nabla_\theta J(\theta) \approx \sum_{t=0}^T \nabla_\omega \log p(\theta|\omega) \mathcal{R}_t^T.
\end{equation}
The resulting algorithms are black-box optimizers, and as such are largely applicable, but can not use the problem structure and have a lot of variance.
Given these insights, we require a way to design algorithms that improve the acting policy stepwise by observing each interaction with the environment.

>>>>

\paragraph{Episode-based updates.} 
A very general optimization approach to this optimization problem are episodic algorithms. 
We take a search distribution $p(\theta|\omega)$ over the parameter space of the policy class $\pi$, and sample acting policies from that distribution. 
The policy class $\pi$ is most often chosen deterministic. 
Using these policies, we sample trajectories $\tau$, and update the search policy using the returns of our sampled roll-outs
\begin{equation}
	\nabla_\theta J(\theta) \approx \sum_{t=0}^T \nabla_\omega \log p(\theta|\omega) \mathcal{R}_t^T.
\end{equation}
The resulting algorithms are black-box optimizers, and as such are largely applicable, but can not use the problem structure and have a lot of variance.
Given these insights, we require a way to design algorithms that improve the acting policy stepwise by observing each interaction with the environment.
